---
title: "Introduction"
author: "[Daviddlhy](https://github.com/Daviddlhy)"
date: "`r lubridate::today('Europe/Paris')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Description 


# Data Description
The data in this package come from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. You can download the data for this assignment here:


## Load Packages

```{r}
library(farsdata)
library(maps)
```


## Included data

Data files included within the package are:

```{r}
list.files(system.file("extdata", package = "farsdata"))
```

## Package Functions

### Function `make_filename`

This function returns file name and path to the data files:

```{r}
yr <- 2013
make_filename(yr)
```

### Function `fars_read_years`

Ancillary function used by `fars_summarize_years`

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This function summarizes yearly accidents data, by month.

```{r}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```

### Function `fars_map_state`

The function displays a state map plot including accidents location
by year

```{r}
state_num <- 49 # Utah
yr <- 2014
fars_map_state(state_num, yr)
```



